The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Add process diagram

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  # TODO remove reshape2 if `melt()` is replaced by`pivot_longer()`
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph"                            # Network analysis and visualization
)

@@

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  # TODO remove reshape2 if `melt()` is replaced by`pivot_longer()`
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph", "DiagrammeR"              # Network analysis and visualization
)

@@

```{r process-diagram}

mermaid("
graph LR
    A[Data collection]-->B[Pre-processing]
    B-->C[Information extraction]
    C-->D[Visualisation]
    C-->B
    D-->E[Results]
")
